On selection of a coupling method to cope with change of priors in one-vs-one classification

### 2025-05-27 paper.tex
oprava pomlcky a rovnice (5)

Distribution shift is an important problem facing machine-learning practitioners  [\cite{zhang2023dive, sugiyama2007covariate}].  One particular way a distribution shift may manifest in classification problems  is when the class priors change between the training set used to train a model, and the data distribution in deployment - the so called label shift [\cite{vsipka2022hitchhiker,lipton2018detecting}]. To make a concrete example, consider a driver assistance system recognizing traffic signs. Suppose a speed limit sign was maliciously altered to indicate 80mph limit instead of 30mph. To avoid being fooled by the alteration, the system could utilize priors. The distribution of traffic signs will change markedly when the car leaves highway and enters streets in a city. It is very unlikely to encounter 80mph limit in a city setting. By taking into account the city priors, a driver assistance is likely to make the proper classification. In general a good classification system will be able to improve its performance when supplied with a new set of class priors that correspond to the true distribution of classes.

>>>>

Distribution shift is an important problem facing machine-learning practitioners  [\cite{zhang2023dive, sugiyama2007covariate}].  One particular way a distribution shift may manifest in classification problems  is when the class priors change between the training set used to train a model, and the data distribution in deployment -- the so called label shift [\cite{vsipka2022hitchhiker,lipton2018detecting}]. To make a concrete example, consider a driver assistance system recognizing traffic signs. Suppose a speed limit sign was maliciously altered to indicate 80mph limit instead of 30mph. To avoid being fooled by the alteration, the system could utilize priors. The distribution of traffic signs will change markedly when the car leaves highway and enters streets in a city. It is very unlikely to encounter 80mph limit in a city setting. By taking into account the city priors, a driver assistance is likely to make the proper classification. In general a good classification system will be able to improve its performance when supplied with a new set of class priors that correspond to the true distribution of classes.
